### 2015-07-02 narrative/naming-service.tex
fixed typo in proposed-work.tex focused naming-service a bit

Given the well documented difficulties with POSIX-compliant naming and our
approach that decomposes data into potentially large number of objects,
we must take a new approach to naming.
Data migration, as a result of system pressures or user/system policies,
further adds to the complexity of managing naming and discovery. Our naming
service must maintain sufficient metadata information, track objects
as they move across storage layers, and facilitates data discovery.

Hierarchical Storage Management (HSM) systems \cite{hsm} offer a strict caching approach
for managing different storage capacities trading off performance for capacity.
By maintaining a single namespace across all tiers, it is possible to list a
single directory view with files stored at different tiers. While this approach
to managing multi-tier storage works for whole files that fit on single logial
devices, it is far from ideal for scientific simulations.

Our goal with this proposal is to offer a similar capability but with a finer
granularity, leveraging the inner structure of scientific data,
and manage data discovery efficiently, where the data may
be split and placed on several storage layers, or may have migrated
based on system pressures or user or system policies. Instead of a single file such as might be used to
store an entire timestep output for a simulation, we will demonstrate extending
this capability to a subset of a single variable level. By shifting to a
finer-grained approach, we will enable more effective use of close/fast/small
storage tiers and prioritize objects with high importance.
Traiditional HSM stores an entire file on a tier making room if
insufficient space is available. With this shift to a partial variable
granularity, a 1 PB output with 200 GB of ``high interest'' data can limit this
costly tier ussage to just 200 GB greatly, improving usability and performance while still
allowing science to be done. This effectively reduces
pressure forcing data migration. Meanwhile, we need to be
able to locate the data should it moves.
Utilizing the description of data (section \ref{}) informed by users and packed by the middleware,
the resulting naming and discovery service will attach the Sirocco
contaier/object/fork/address tuple with a special attribute indicating that
this record is of ``high interest'' strongly encouraging keeping the record
in close/fast/small storage as long as possible.

The challenge for discovery is that potentially, data will migrate from where
it is initially stored to a new location within the storage system. Sirocco
offers an ability to search for data that has moved as well as forcing a
particular resilience-based replica be the ``authoritative'' version. We will
investigate if the current Sirocco functionality is capable of supporting the
new operating modes we wish to offer. Initial expectations suggest having
bounded time guarantees for finding data are critical for offering the quality
of service guarantees we wish to offer. Some potential approaches can build on
CRUSH~\cite{ceph} from Ceph to offer a map of where to search for data
sequentially. Given our multiple storage tiers, we would extend this using some
search limiting mechanism indicating to shift to the next tier to continue
searching because the requested data never made it to this location. This new
work will be an expansion of Sirocco's currently planned features.

The overriding theme for this proposal of providing a cooperative relationship
between the user and the storage system extends into this area as well. In
order for the user to negotiate with the storage system for data
quality/retrieval time tradeoff, additional data is required. Providing this
functionality requries the naming service be able to both return a list of data
versions, but also some indication of data quality and estimated retrieval time
for each. This estimate will be disucssed elsewhere in this proposal.

Structurally, the traditional POSIX naming service offeriing a hierarchical
space consisting of directories and files may be maintained for backwards
compatibility. However, this view will not offer the same strict semantics
POSIX requires. We must break these strict semantics to address scalability
problems because of the serialized access to a single source for creating and
accessing files.  Several efforts~\cite{giga+,pvfs,others} have worked to
reduce this contention by doing things like reducing the serialized scope to a
single directory or subtree. While these approaches help, they do not address
this key scalability limitation. Instead, we ar willing to offer a short
duration to eventually consistent POSIX view to offer the performance and
consistency requirements an exascale application demands.

While pure object stores, such as those popular in the big data
domain~\cite{memcached,others} avoid this bottleneck by strictly offering an
object ID with the application required to manage how this ID maps to something
of interest. This approach of removing the metadata service from the system
level completely can work well for scale out applications where data is created
or consumed by a single process at a time rather than potentially O(1 million)
processes all actively collectively for a single ``object''. To address this
case, having some system integrated metadata services to associate names with
these object is a preferable solution. While it will not have the same
synchronous consistency semantics as POSIX, we will offer something as close as
possible to address legacy application and command-line style data access and
migration to other storage types using these POSIX semantics.

@@

In addition to the basic naming and data tracking operations, we will also need
to incorporate authorization capabilities. Sirocco currently integrates with a
Kerberos service for authentication and authorization. Given a capability
ticket, a user can access different objects as needed. This ticket structure
offers protection services typically offered on POSIX directories and files,
but can do it at the fork level instead. This allows a reduced quality data
version to be available for the general users while the high-quality version
would be limited to the data creator. This and other considerations for
security must be incorporated into the entire naming and metadat service.

@@

\item Milestone 2: Demonstrate a time bounded search approach for finding data
within the storage system to identify data the current location and retrieval
performance characteristics for data since migration. This will update the
cached information in the metadata service to short-circuit future requests for
the data presuming that it does not migrate again.

>>>>

Given the well documented difficulties with POSIX-compliant naming and our
approach that decomposes what would be a single file into potentially large
number of objects, we must take a new approach to naming.  Data migration, as a
result of system pressures or user/system policies, further adds to the
complexity of managing naming and discovery. Our naming service must maintain
sufficient metadata information, track or be able to find objects as they move
across storage layers, and facilitates data discovery.

Hierarchical Storage Management (HSM) systems~\cite{hsm} offer a strict caching approach
for managing different storage capacities trading off performance for capacity.
By maintaining a single namespace across all tiers, it is possible to list a
single directory view with files stored at different tiers. While this approach
to managing multi-tier storage works for whole files that fit on single logial
devices, it is far from ideal for scientific simulations.

Our goal with this proposal is to offer a similar capability but with a finer
granularity leveraging the inner structure of scientific data. It must also
handle data discovery efficiently for cases where data is spread across several
storage layers or some of those pieces may have migrated based on system
pressures or user or system policies. Instead of a single file, such as might
be used to store an entire timestep output for a simulation, we will
demonstrate a metadata service with naming at the science variable level, but
with an associated list of all of the variable pieces and potentially different
versions stored throughout the storage system. By shifting to a finer-grained
approach, we will enable more effective use of close/fast/small storage tiers
and prioritize objects with high importance.  Traiditional HSM stores an entire
file on a tier making room if insufficient space is available.  With this shift
to a partial variable granularity, a 1 PB output with 500 GB of ``high
interest'' data can limit this costly tier usage to just 500 GB greatly
improving storage availability in the close/fast/small tier and focus
performance/capacity costs to get the most science from from the platform.  By
only placing ``high interest'' data in the close/fast/small tier, we will
effectively reduce pressure forcing data migration hurting both writing
performance and the later data analytics required for generating scientific
insights.  Sirocco identifies a data segment using a
contaier/object/fork/address tuple that can have associated attributes. We will
both add a special attribute indicating that this record is of ``high
interest'' as well adapting the migration mechanisms to use this attribute, if
present, to strongly encouraging keeping the record in close/fast/small storage
as long as possible.

Meanwhile, we need to be able to locate or ``discover'' the data should it
move.  The challenge for discovery is that potentially, data will migrate from
where it is initially stored to a new location within the storage system.
Sirocco offers an ability to search for data that has moved as well as forcing
a particular resilience-based replica be the ``authoritative'' version
migrating the data to a particular location. We will investigate if the current
Sirocco functionality is capable of supporting the new operating modes we wish
to offer. Initial expectations suggest having bounded time guarantees for
finding data are critical for offering the quality of service guarantees we
wish to offer. Some potential approaches can build on CRUSH~\cite{ceph} from
Ceph to offer a map of where to search for data sequentially. Given our
multiple storage tiers, we would extend this using some mechanism to shift to
the next tier to continue searching because the requested data never made it to
this location. This new work will be an expansion of Sirocco's currently
planned features.

The overriding theme for this proposal of providing a cooperative relationship
between the user and the storage system extends into this area as well.
Negotiating the data quality/retrieval time tradeoff reuqires additional data.
Providing this functionality requries the naming service be able to both return
a list of data versions and an indication of data quality. This will be
combined with a retrieval time estimate for each verstion by the middleware to
determine what data version should be retrieved.  This estimate will be
disucssed elsewhere in this proposal.

Structurally, the traditional POSIX naming service offeriing a hierarchical
space consisting of directories and files may be maintained for backwards
compatibility. However, this view will not offer the same strict semantics
POSIX defines. We must break these strict semantics to address scalability
problems forced by the serialized access to a single source for creating and
accessing files.  Several efforts~\cite{giga+,pvfs,others} have worked to
reduce this contention by doing things like reducing the serialized scope to a
single directory or subtree. While these approaches help, they do not address
this key scalability limitation of serialized access--even if the metadata
service is spread across multiple nodes. Instead, we will offer a
short duration to consistency POSIX view to offer the performance and
consistency requirements an exascale application demands.

While pure object stores, such as those popular in the big data
domain~\cite{memcached,others} avoid this bottleneck by strictly offering an
object ID with the application required to manage how this ID maps to something
of interest. This approach of removing the metadata service from the system
level completely can work well for scale out applications where data is created
or consumed by a single process at a time or just in a work queue rather than
potentially O(1 million) processes all actively collectively for a single
``object''. To address this case, having some system integrated metadata
services to associate names with these object is a preferable solution. While
it will not have the same synchronous consistency semantics as POSIX, we will
offer something as close as possible to address legacy application and
command-line style data access and migration to other storage types using these
POSIX semantics.

@@

In addition to the basic naming and data tracking operations, we will also need
to incorporate authorization capabilities. Sirocco currently integrates with a
Kerberos service for authentication. Given a capability ticket, a user can
access different objects as needed. This ticket structure offers protection
services typically offered on POSIX directories and files, but can do it at the
fork level instead. This allows a reduced quality data version to be available
for the general users while the high-quality version would be limited to the
data creator. This and other considerations for security must be incorporated
into the entire naming and metadata service.

@@

\item Milestone 2: Demonstrate a time bounded search approach for finding data
within the storage system to identify data and the current location.  This will
update the cached information in the metadata service to short-circuit future
requests for the data presuming that it does not migrate again soon.
